### 2017-12-12 Paper/main.tex
Updates from ShareLaTeX

\documentclass[twocolumn]{article}
\usepackage{array,url,kantlipsum}
\usepackage{lmodern}
\usepackage{tikz}
\usepackage{capt-of}
\usepackage{biblatex}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{breqn}

@@

Then we built a NN out of it which set as input the lagged stock price and as output the current error term \ref{}.

@@

\newpage
\begin{figure}
    \centering
    \includegraphics[width=1\linewidth, ]{Paper/images/NN_plot}
    \caption{Plot of the aggregate P/L per stock}
    \label{nn_portfolio}
\end{figure}

>>>>

\documentclass[twocolumn]{article}
\usepackage{array,url,kantlipsum}
\usepackage{lmodern}
\usepackage{tikz}
\usepackage{capt-of}
\usepackage{biblatex}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{breqn}
\usepackage{rotating}

@@

Then we built a NN out of it which set as input the lagged stock price and as output the current error term \ref{NN_plot}.

@@

\newpage
\newpage

\begin{sidewaysfigure*}[htbp]
\centering
\includegraphics[width=\linewidth, height=\textheight,keepaspectratio]{Paper/images/NN_plot.png}
\caption[short]{\text{Plot of the Neural Network forecasting AAXN current errors}}
\label{NN_plot}
\end{sidewaysfigure*}
